Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-18 01-clean.Rmd
Add HDI

>>>>

This data set was downloaded from <http://hdr.undp.org/en/indicators/137506#> in November 2021, and shared here under the terms of use <http://hdr.undp.org/en/content/copyright-and-terms-use>.

```{r}
hdi <- read_csv("data-raw/HDI/Human Development Index (HDI).csv", skip = 5) %>% 
  # Get rid of weird empty columns
  select(c(1, 2, seq(3, 61, by = 2)), country = Country) %>%
  # Keep countries only
  drop_na(`HDI Rank`) %>% 
  select(-`HDI Rank`) %>% 
  pivot_longer(-1, names_to = "year", values_to = "hdi") %>% 
  mutate(across(year:hdi, as.numeric)) %>% 
  filter(year >= 2000)

# Replace broken string
hdi$country[46]
hdi$country[46] <- "Côte d’Ivoire"

# Harmonise names
hdi <- hdi %>% 
  mutate(country = countryname(country))
```
